\documentclass[preprint,authoryear,semicolon,12pt]{elsarticle}
\usepackage{cmap}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{array}
\usepackage{xcolor}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage[final, defaultcolor=red]{changes}
\usepackage{xr}
\usepackage[colorlinks=true]{hyperref}

%----Helper code for dealing with external references----
% (by cyberSingularity at http://tex.stackexchange.com/a/69832/226)
% see also https://www.overleaf.com/learn/how-to/Cross_referencing_with_the_xr_package_in_Overleaf

\usepackage{xr}
\makeatletter

\newcommand*{\addFileDependency}[1]{% argument=file name and extension
\typeout{(#1)}% latexmk will find this if $recorder=0
% however, in that case, it will ignore #1 if it is a .aux or 
% .pdf file etc and it exists! If it doesn't exist, it will appear 
% in the list of dependents regardless)
%
% Write the following if you want it to appear in \listfiles 
% --- although not really necessary and latexmk doesn't use this
%
\@addtofilelist{#1}
%
% latexmk will find this message if #1 doesn't exist (yet)
\IfFileExists{#1}{}{\typeout{No file #1.}}
}\makeatother

\newcommand*{\myexternaldocument}[1]{%
\externaldocument[supp-]{#1}%
\addFileDependency{#1.tex}%
\addFileDependency{#1.aux}%
}
%------------End of helper code--------------

% Links to the external document
\myexternaldocument{supplementary}


% Remove info about journal submission
\journal{}
\makeatletter
\def\ps@pprintTitle{%
  \let\@oddhead\@empty
  \let\@evenhead\@empty
  \def\@oddfoot{\reset@font\hfil\thepage\hfil}
  \let\@evenfoot\@oddfoot
}
\makeatother

\graphicspath{ {./figures/} }

\newcommand{\at}{@}
\newcommand{\tofix}[1]{\textcolor{magenta}{#1}}
\input{numbers/combined}

\geometry{a4paper, total={170mm,257mm}, left=20mm, top=20mm}
\parindent = 0 cm

\begin{document}

\begin{frontmatter}

% Title

\title{Sensorimotor brain-computer interface performance depends on signal-to-noise ratio but not connectivity of the mu rhythm in a multiverse analysis of longitudinal data}

\input{authors}
    
% Abstract

\begin{abstract}
    \input{sections/abstract}
\end{abstract}

\end{frontmatter}

%% Main text

\newpage

\input{sections/introduction}

\input{sections/methods}

\input{sections/results}

\input{sections/discussion}

\input{sections/conclusion}

\section*{Data and Code Availability}

EEG recordings are publicly available at \texttt{\url{https://doi.org/10.6084/m9.figshare.13123148}}, and a detailed description of the dataset is provided in \citep{Stieger2020_analysis, Stieger2021_dataset}. Analysis scripts are available at \texttt{\url{https://github.com/ctrltz/bci-brain-connectivity}}. Preprocessing data that are necessary to reproduce the analysis (indices of bad trials, channels, and ICA components; ICA weights, excluded sessions, etc.) are available at \texttt{\url{https://osf.io/tcvyd}}.

\section*{CRediT Authorship Contribution Statement}

\textbf{Nikolai Kapralov:} Conceptualization, Data curation, Formal analysis, Investigation, Methodology, Software, Visualization, Writing – original draft, Writing – review \& editing. \textbf{Mina Jamshidi Idaji:} Validation (Code Review), Writing – review \& editing. \textbf{Tilman Stephani:} Methodology, Validation (Code Review), Writing – review \& editing. \textbf{Alina Studenova:} Validation (Code Review), Writing – review \& editing. \textbf{Carmen Vidaurre:} Software, Writing – review \& editing. \textbf{Tomas Ros:} Writing – review \& editing. \textbf{Arno Villringer:} Funding acquisition, Supervision, Writing – review \& editing. \textbf{Vadim Nikulin:} Conceptualization, Investigation, Methodology, Project administration, Supervision, Writing – Original Draft, Writing – review \& editing.

\section*{Acknowledgments}

We would like to thank the authors of the dataset for making it publicly available and James Stieger in particular for providing additional information about the dataset on request. C.V. was funded by the Spanish Ministry of Science, Innovation and Universities, ref. number PID2020-118829RB-I00.

\bibliographystyle{elsarticle-harv} 
\bibliography{main}

\end{document}
